% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
%-----------------------------------------------------------
%\usepackage{fullpage}
\usepackage{shading}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{center}
\textbf{\Large David Ko}\\
vsxx.github.io
\end{center}
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
%\textbf{\Large David Ko}  & 713-261-4667\\
3102 Timber Village Dr. &  713-261-4667 \\
Houston, TX 77068 & davidpeterko@gmail.com\\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Education}
\begin{itemize}
\item
	\ressubheading{University of Texas}{Austin, TX}{BS, Computer Science}{August 2009 - August 2015}
	\begin{itemize}
			\resitem{Relevant courses: Principles of Computer Systems (OS), Information Assurance and Security, Computer Security, Cryptography, Data Visualization and Warehousing.}
	\end{itemize}
\end{itemize}

\resheading{Work Experience}
\begin{itemize}
\item
	\ressubheading{M\&D Distributors}{Humble, TX}{Internship for IT Security}{June 2014 - August 2014}
	\begin{itemize}
			\resitem{Maintained network and computer security in IT.}
			\resitem{Used Various resources and software such as Spiceworks, WatchGuard, and WireShark.}
	\end{itemize}

\end{itemize}

\resheading{School Projects}
\begin{itemize}
\item
	\ressubheading{SpectraVu Medical}{Vancouver, BC}{Engineering Physics Project Lab, APSC 479}{Sep. 2001 - Apr. 2002}
	\begin{itemize}
		\resitem{Designed and implemented a digital video processing system for lung cancer imaging,}
	\end{itemize}

\item
	\ressubheading{Analog Circuit Design and MOSFET Device Design}{}{Semiconductor Devices Course, EECE 480}{Sep. 2001 - Apr. 2002}
	\begin{itemize}
		\resitem{Designed a high-frequency cascode amplifier, simulated it using HSPICE, and did layout using Cadence Virtuoso Layout software.  Manufactured on a Gennum GA911 chip.}
		\resitem{Designed and simulated a deep sub-micron (~70 nm channel) MOSFET using MEDICI.}
	\end{itemize}

\item
	\ressubheading{Low-cost Optoelectronic Localizer}{}{Engineering Physics Project Lab, APSC 459}{Sep. 2000 - Apr. 2001}
	\begin{itemize}
		\resitem{Worked on the LoCOL (Low-cost Optoelectronic Localizer) project in a team of three.}
		\resitem{Programmed a PIC microcontroller to control the timing of the three CCD cameras.}
		\resitem{Designed power supply and re-built electrical circuits for the CCD sensors, processors.}
		%\resitem{Helped build an enclosure for optics and electronics in the Student Machine Shop.}
	\end{itemize}

\item
	\ressubheading{Other Projects}{}{UBC and at home}{1999-2000}
	\begin{itemize}
		\resitem{Designed and debugged a digital voltmeter using a Motorola 68000 processor.}
		\resitem{Added features to the digital voltmeter including scrolling text, and a warning buzzer, which won 3rd place in the IEEE Voltmeter Competition.}
		\resitem{Constructed and debugged a digital clock on a PCB for PHYS 159.}
		\resitem{Built an AM short-wave radio at home, on a 2" $\times$ 2.5'' piece of breadboard.}
	\end{itemize}

\end{itemize}

\resheading{Awards}
	\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		Faculty of Engineering Scholarship (\$2,300) & 2002\\
		Ontario Graduate Scholarship (OGS) (\$15,000) & 2002-2003\\
		Industrial NSERC Undergraduate Research Award (\$4500) & 2002\\
		UBC OSI (Outstanding Student Initiative) Entrance Scholarship (\$10,000) & 1997-2002\\
		Engineering Physics 50th Anniversary Scholarship (\$600) & 2001\\
		Anne. M. Mack Scholarship (\$500) & 2001\\
		NSERC Undergraduate Student Research Award (\$4000) & 2000\\
		United Food and Commercial Workers Union, Local 1518 Scholarship (\$1000) & 1998\\
		Top Senior Math Student Award & 1997\\
		B.C. Provincial Exam Scholarship (\$1000) & 1997\\
		B.C. Government Passport to Education (\$800) & 1997\\
		James Whiteside Elementary Parent Advisory Committee Award (\$200) & 1997\\
\end{tabular*}

\resheading{Skills}

\begin{description}
\item[Languages:]
C/C++, \LaTeX, Java, SPICE, MEDICI (TCAD), VHDL/VHDL-AMS, 68000 and PIC Assembly
\item[Operating Systems:]
Linux (Debian), Solaris, UNIX, MacOS X, Windows 95/98/NT/2000/XP
\item[Applications:]
Mathematica, MatLab, GNU Octave, LabVIEW, Cadence, \LaTeX, OpenOffice, MS Office XP, OrCAD schematic capture \& PCB layout, Altera MAX+PlusII VHDL FPGA Design
\item[Lab Skils:]
Digital/Analog Scopes, Spectrum Analyzer, Function Generators
\item[Fab Skills:]
PECVD and sputtering deposition, UV lithography, wet etch, dry etch (RIE), mask aligner, step profiler, ellipsometry, infrared spectroscopy, x-ray diffraction
\item[Miscellaneous:]
software configuration management, strong verbal and written communication skills, excellent troubleshooting and debugging skills, exceptional problem solving skills, good teams skills
\end{description}

\resheading{Interests}

\begin{description}
\item[Academic:] Solid state devices,  nanotechnology, photonics, microcontrollers, RF/wireless
\item[Sports:] Playing hockey and swimming
\item[Computers:] Currently maintain two official Debian Linux packages, Mozilla beta tester, enjoy using and learning Linux systems, Building electronics projects at home, and writing JAVA software
\item[Musical:] Playing guitar and piano
\item[Membership:] Student member of IEEE since 1998, Materials Research Society member since 2002
\item[Other:] Reading novels
\end{description}

\end{document}
