% Cover letter using letter.cls
\documentclass{letter} % Uses 10pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8.5in    % text height can be bigger for a longer letter
\oddsidemargin=0pt   % leftmargin is 1 inch
\textwidth=6.5in     % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{David Peter Ko}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
 
\begin{letter}{Hewlett-Packard \\
11445 Compaq Center West Dr. \\
Houston, TX 77070 }


\begin{center}
{\large\bf David Peter Ko} 
\end{center}
\medskip\hrule height 1pt
\begin{center}
{3102 Timber Village Dr. \\  Houston, TX 77068 \\ 713-261-4667} 
\end{center} \vfill % forces letterhead to top of page
 
 
\opening{Dear Hewlett-Packard:} 
 
\noindent I am a new graduate from the University of Texas and came across your job opening on Indeed.com. I am very interested in what your company has to offer. I graduated this past summer with a Bachelor's of Science in Computer Science with high interest in software engineering and development. 
 
\noindent The job description for Software Designer is what really caught my attention. HP is a very reputed company and I am very willing to begin my career there in such a great environment. This is the perfect opportunity to be able to grow and learn as much as possible at your company.  
 
\noindent Attached to my application is my resume in pdf format and it includes a link to my portfolio at the top if you would like to see my work I have done at UT and my own personal non-academic projects. Thank you for your time and I hope to hear from you soon! 
 
\closing{Sincerely yours,} 
 

 
\encl{Resume}					% Enclosures

\end{letter}
 

\end{document}

